\cvsection{Work Experience}

\begin{cventries}
	\cventry
		{Software Engineer II --- Azure Observability}
		{Microsoft}
		{Redmond, Washington}
		{August 2021 - March 2023}
		{\begin{cvitems}
			\item Contributed to the OpenTelemetry .NET SDK and worked with members of the community.
			\item Primary contributor, approver role, \& initiator of a community OpenTelemetry Demo --- 8+ languages, 1400+ stars, 100+ contributors.
			\item Used BenchmarkDotNet to identify how many buckets a histogram must have for binary search to outperform linear search.
			\item Added the capture of minimum and maximum value to histograms, ensured bounds in ascending order \& distinct.
			\item Managed daily repository PR \& issue monitoring and maintained alignment with API requirements \& release timelines.
			\item Ensured thread-safe testing \& addressed community-reported bugs promptly while maintaining effective communication within the team.
		\end{cvitems}}
		
	\cventry
		{Software Engineer --- Edge Experimentation}
		{Microsoft}
		{Redmond, Washington}
		{June 2019 - August 2021}
		{\begin{cvitems}
			\item Enabled safe feature experiments with a C\# serverless PR approval bot enforcing rules.
			\item Developed an internal system for cataloging \& monitoring 2000+ product features to ensure interoperability.
			\item Transitioned from daily email reports to a dashboard, reducing review time from hours to minutes per week.
			\item Parsed daily C++ code from Edge and Chromium to identify these feature struct definitions and included platforms.
			\item Implemented ingestion and decoding of Chrome's experiment service protobuf into blob storage \& database every 15 minutes.
		\end{cvitems}}

	\cventry
		{Software Developer --- Summer Student}
		{Martello Technologies}
		{Kanata, Canada}
		{April 2018 - August 2018}
		{\begin{cvitems}
			\item Revamped a legacy dashboard with reusable custom UI components in Vue.js \& a REST API.
			\item Created a suite of asynchronous tests for CRUD operations on containers \& devices using Mocha.
			\item Presented the project's progress every 2 weeks to the management team, shareholders \& other developers.
		\end{cvitems}}

	\cventry
		{Teaching Assistant --- Fundamentals of Web Applications \& Introduction to Computer Science II}
		{Carleton University: School of Computer Science}
		{Ottawa, Canada}
		{September 2016 - December 2018}
		{\begin{cvitems}
			\item Collaborated with other teaching assistants to both create rubrics \& fairly grade assignments.
			\item Conducted weekly workshops surrounding the course's content \& provided assistance during my office hours.
		\end{cvitems}}
\end{cventries}
